correlationstuff

### 2024-01-31 Paper1.Rmd
made cor stuff pdf document neater

# all lms after FA
```{r, echo=FALSE}
# 3 linear models - 1) lm with demographic variables except age and State
m1_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores)
# Print model summary
#summary(m1_demo)
#plot(m1_demo)

>>>>

# all lms after FA
```{r, echo=FALSE}
# 3 linear models - 1) lm with demographic variables except age and State

m1_demo <- lm(Risky_Nuclear ~ Uppercaste + Male + Hindu + Urban, data = fascale_scores)

# Print model summary
#summary(m1_demo)
#plot(m1_demo)

### 2024-01-31 corstuff.Rmd
made cor stuff pdf document neater

---
title: "correlationstuff"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  keep_md: yes
---

@@

# EDIT :  Kahan scale EFA  
```{r, echo=FALSE}

@@

print.psych(kahan.fa, cut = 0.4, sort = TRUE)

@@

@@

```
# Confirmatory Factor Analysis(CFA): Kahan Scale

@@

```{r}
# binding ecopol with alternative Kahan scale score 
fascale_scores2 <-cbind(Kscalescores, scores1)  %>%
  rename(Pdevelop = MR1)%>%
  rename(Ndevelop = MR2)

fascale_scores2

@@

# Lms with alt Kahan scores 
```{r, echo = FALSE}

@@

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(m1_kahan2, m1_ecopol2, m1_allscales2, 
          title = "Results from 3 linear regression models",
          type = "latex"
)
cat("\\endgroup")

@@

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(m1_kahan, m1_allscales, 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

@@

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(m1_ecopol, m1_allscales, 
          title = "Results from 2 linear regression models",
          type = "latex"
)
cat("\\endgroup")

```
\newpage

@@

fascale_scores

fascale_scores2

>>>>

---
title: "correlationstuff"
output:
  pdf_document:
    toc: yes
    toc_depth: 2
    keep_tex: yes
  header-includes:
  - \usepackage{dcolumn}
  - \usepackage{array}
  - "\\usepackage{placeins}"
  - \usepackage{pdflscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  keep_md: yes
---

@@

\blandscape
# Kahan scale EFA  
```{r, echo=FALSE}

@@

#print.psych(kahan.fa, cut = 0.4, sort = TRUE)

@@

\elandscape

@@

# Confirmatory Factor Analysis(CFA): Kahan Scale

@@

```{r, echo=FALSE}
# binding ecopol with alternative Kahan scale score 
fascale_scores2 <-cbind(Kscalescores, scores1)  %>%
  rename(Pdevelop = MR1)%>%
  rename(Ndevelop = MR2)

@@

\newpage
# Lms with alt Kahan scores 
```{r, echo = FALSE}

@@

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(m1_kahan2, m1_ecopol2, m1_allscales2, 
          title = "Alternative Kahan Scores(mean acorss fixed factors)",
          type = "latex"
)
cat("\\endgroup")

@@

cat("\\begingroup")
cat("\\setlength{\\tabcolsep}{1pt}")
cat("\\renewcommand{\\arraystretch}{0.7}")
stargazer(m1_kahan,m1_ecopol, m1_allscales, 
          title = "Lms with CFA Kahan",
          type = "latex"
)
cat("\\endgroup")

@@

@@

#fascale_scores

#fascale_scores2
